Working Title: Predicting Customer Behavior Using a Portuguese Financial Institution Dataset 

### 2024-06-14 code/eda-code/eda - my version.qmd
New plots, Updated Manuscript

# Setup
Necessary libraries for this script.
```{r}
library(here) 
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
```

Load the data.

@@

```{r}
mydata |>
  ggplot(aes(job))+
  geom_bar()

mydata |>
  ggplot(aes(education))+
  geom_bar()

mydata |>
  ggplot(aes(marital))+
  geom_bar()
```

>>>>

# Setup
Necessary libraries for this script.
```{r}
library(here) 
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
library(tidyr)
library(forcats)
```

Loading the data.

@@

```{r}
p6 = mydata |>
  ggplot(aes(x=fct_infreq(job)))+
  geom_bar() +
  coord_flip()

p7 = mydata |>
  ggplot(aes(education))+
  geom_bar()

p8 = mydata |>
  ggplot(aes(marital))+
  geom_bar()

p6
p7
p8

figure_file = here("results", "figures", "job-barchart.png")
ggsave(filename = figure_file, plot=p6) 
figure_file = here("results", "figures", "education-barchart.png")
ggsave(filename = figure_file, plot=p7) 
figure_file = here("results", "figures", "marital-barchart.png")
ggsave(filename = figure_file, plot=p8) 
```

Quick look at positive cases vs negative cases of outcome variable (y_termSubscribed)
```{r}
plot(mydata$y_termSubscribed)
```

Lets see how the age demographic differs between the population that subscribed to a term (y_termsubscribed=yes) vs the general population.

```{r}
p9 = mydata |>
  filter(y_termSubscribed == "yes") |>
  ggplot(aes(age))+
  geom_bar()+
  labs(title = "yes")

p10 = mydata |>
  ggplot(aes(age))+
  geom_bar()+
  labs(title = "yes/no")

p9
p10
```

Now, lets assess the highest job categories that are labeled as subscribing to a term.

```{r}
p11 = mydata |>
  filter(y_termSubscribed == "yes") |>
  ggplot(aes(x=fct_infreq(job)))+
  geom_bar()+
  coord_flip()+
  labs(title = "Term Subscribed = yes")

p11
```

### 2024-06-14 code/processing-code/processingfile-v1 - my version.qmd
New plots, Updated Manuscript

```{r}
library(readxl) #for loading Excel files
library(dplyr) #for data processing/cleaning
library(tidyr) #for data processing/cleaning
library(skimr) #for nice visualization of data 
library(here) #to set paths
```

@@

Examning metadata by accessing the codebook

@@

We are mainly converting character variables into factors so we can do some categorical analysis
```{r}
d1 = rawdata |> 
  mutate(job = as.factor(job)) |>
  mutate(marital = as.factor(marital)) |>
  mutate(education = as.factor(education)) |>
  mutate(default = as.factor(default)) |>
  mutate(housing = as.factor(housing)) |>
  mutate(loan = as.factor(loan)) |>
  mutate(education = as.factor(education)) |>
  mutate(contact = as.factor(contact)) |>
  mutate(month = as.factor(month)) |>
  mutate(poutcome = as.factor(poutcome)) |>
  mutate(y = as.factor(y))

>>>>

```{r}
library(readxl) 
library(dplyr) 
library(tidyr) 
library(skimr) 
library(here) 
```

@@

Examining metadata by accessing the codebook.
This codebook was taken directly from the data repository housing the chosen dataset.
The decision was made to keep this in a separate xlsx file from the dataset so that the dataset could remain in the identical form in which it was sourced (CSV format).

@@

We are mainly converting character variables into factors so we can do some categorical analysis.
I had initially included converting months to a numeric variable but realized that it was fine as a factor variable.
```{r}
d1 = rawdata |> 
  mutate(job = as.factor(job)) |>
  mutate(marital = as.factor(marital)) |>
  mutate(education = as.factor(education)) |>
  mutate(default = as.factor(default)) |>
  mutate(housing = as.factor(housing)) |>
  mutate(loan = as.factor(loan)) |>
  mutate(education = as.factor(education)) |>
  mutate(contact = as.factor(contact)) |>
  mutate(month = as.factor(month)) |>
  mutate(poutcome = as.factor(poutcome)) |>
  mutate(y = as.factor(y))

colnames(d1)[17] <- "y_termSubscribed"

### 2024-06-14 products/manuscript/Manuscript.qmd
New plots, Updated Manuscript

There are 45,212 records, and includes: age, marital status, job, education,details related to the phone call, as well as answers related to questions about past credit history. Additionally, the classification variable is whether or not the person subscribed to a term deposit. There are 16 features in total.

@@

@tbl-summarytable shows a summary of the data.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable1.rds")
knitr::kable(resulttable)
```

@@

@fig-result shows a scatter plot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Age and bank account balance stratified by marital status"
#| echo: FALSE
knitr::include_graphics(here("results","figures","age-balance-stratified.png"))
```

>>>>

There are 45,212 records, and includes: age, marital status, job, education,details related to the phone call, as well as answers related to questions about past credit history. Additionally, the classification variable is whether or not the person subscribed to a term deposit. There are 17 features in total.

Among the variables are a handful of features relating to the marketing campaign itself. For example, included are the day, month, and duration of the call, the number of contacts performed during the campaign (campaign), the number of days since the client was last contacted (pdays), the number of contacts performed before this campaign (previous), and finally the outcome of precious marketing campaigns (poutcome).

@@

@fig-result shows a boxplot figure comparing balance levels across job types.

```{r}
#| label: fig-result
#| fig-cap: "Job type and bank account balance"
#| echo: FALSE
knitr::include_graphics(here("results","figures","job-balance-scatter.png"))
```

@fig-result1 shows a bar chart showing education levels of the data.

```{r}
#| label: fig-result1
#| fig-cap: "Education level"
#| echo: FALSE
knitr::include_graphics(here("results","figures","education-barchart.png"))
```

@fig-result2 shows a scatter plot figure produced by one of the R scripts.

```{r}
#| label: fig-result2
#| fig-cap: "Age and bank account balance stratified by marital status"
#| echo: FALSE
knitr::include_graphics(here("results","figures","age-balance-stratified.png"))
```

@@
